---
title: "Assignment_2"
author: "Archana Gadicharla"
date: "2024-09-23"
output:
  pdf_document: default
  html_document: default
---

## QUESTION
## The Weigelt Corporation has three branch plants with excess production capacity. Fortunately, the corporation has a new product ready to begin production, and all three plants have this capability, so some of the excess capacity can be used in this way. This product can be made in three sizes–large, medium, and small–that yield a net unit profit of $420, $360, and $300, respectively. Plants 1, 2, and 3 have the excess capacity to produce 750, 900, and 450 units per day of this product, respectively, regardless of the size or combination of sizes involved. The amount of available in-process storage space also imposes a limitation on the production rates of the new product. Plants 1, 2, and 3 have 13,000, 12,000, and 5,000 square feet, respectively, of in-process storage space available for a day’s production of this product. Each unit of the large, medium, and small sizes produced per day requires 20, 15, and 12 square feet, respectively. Sales forecasts indicate that if available, 900, 1,200, and 750 units of the large, medium, and small sizes, respectively, would be sold per day. At each plant, some employees will need to be laid off unless most of the plant’s excess production capacity can be used to produce the new product. To avoid layoffs if possible, management has decided that the plants should use the same percentage of their excess capacity to produce the new product. Management wishes to know how much of each of the sizes should be produced by each of the plants to maximize profit.

```{r}
data_matrix <- matrix(c(900,"$420",20,1200, "$360",15,750,"$300",12),ncol =3,byrow=TRUE)

# Assigning appropriate labels to columns and rows
colnames(data_matrix) <- c("Sales","Profit","Material")
rownames(data_matrix) <- c("Large","Medium","Small")

# Converting the matrix to a table format for better readability
result_table <- as.table(data_matrix)
result_table
```

###To address the problem, we need to establish the objective function, constraints, direction, and constants.

### Objective Function The aim of the objective function is to:

MaxZ=420(X1+X2+X3)+360(Y1+Y2+Y3)+300(Z1+Z2+Z3)

### Rewriting the objective function we have,

MaxZ=420X1+360Y1+300Z1+420X2+360Y2+300Z2+420X3+360Y3+300Z3

### Constraints The constraints are represented as follows:

X1+Y1+Z1≤750 X2+Y2+Z2≤900 X3+Y3+Z3≤450 20A1+15K1+12H1<=13000 20X2+15Y2+12Z2≤12000 20X3+15Y3+12Z3≤5000

###Also,

X1+X2+X3≤900 Y1+Y2+Y3≤1200 Z1+Z2+Z3≤750

### Non-Negativity Constraints All variables must be non-negative: 
X1,X2,X3,Y1,Y2,Y3,Z1,Z2,Z3≥0

### Additional Equations We also have the following equalities: 
X1+Y1+Z1=750 
X2+Y2+Z2=900
X3+Y3+Z3=450 

900X1+900Y1+900Z1−750X2−750Y2−750Z2+0X3+0Y3+0Z3=0 
0X1+0Y1+0Z1+450X2+450Y2+450Z2−900X3−900Y3−900Z3=0 
450X1+450Y1+450Z1+0X2+0Y2+0Z2−750X3−750Y3−750Z3=0


###Solution To address this problem using R, we need to utilize the “lpsolve” library.

```{r}
#install.packages("lpSolve")
library("lpSolve")
```


###Defining the Objective Function - obj.fun

```{r}
obj.fun <- c(420,360,300,420,360,300,420,360,300)
```


###Defining the Constraints - con.fun

```{r}
con.fun <- matrix(c(1,1,1,0,0,0,0,0,0,
                       0,0,0,1,1,1,0,0,0,
                       0,0,0,0,0,0,1,1,1,
                       20,15,12,0,0,0,0,0,0,
                       0,0,0,20,15,12,0,0,0,
                       0,0,0,0,0,0,20,15,12,
                       1,0,0,1,0,0,1,0,0,
                       0,1,0,0,1,0,0,1,0,
                       0,0,1,0,0,1,0,0,1,
                       900,900,900,-750,-750,-750,0,0,0,
                       0,0,0,450,450,450,-900,-900,-900,
                       450,450,450,0,0,0,-750,-750,-750),nrow = 12,byrow = TRUE)
con.fun
```

###Defining the Direction of the constraints - dir.fun

```{r}
dir.fun <- c('<=',

           '<=',
           
           '<=',
           
           '<=',
           
           '<=',
           
           '<=',
           
           '<=',
           
           '<=',
           
           '<=',
           '=',
           '=',
           '=')
```


###Definiing the constants that means the right hand side values - rhs.fun

```{r}
rhs.fun <- c(750,
         900,
         450,
         13000,
         12000,
         5000,
         900,
         1200,
         750,
         0,
         0,
         0)
```


###Using the lp function to solve the problem by focusing on the goal of making the most profit.

```{r}
max_cost=lp('max',obj.fun,con.fun,dir.fun,rhs.fun)
max_cost
```

###Using the lp function again to calculate the values of the variables mentioned earlier.

```{r}
max_cost$solution
```

```{r}
max_cost$solution[1]
```

```{r}
max_cost$solution[2]
```

```{r}
max_cost$solution[3]
```

```{r}
max_cost$solution[4]
```

```{r}
max_cost$solution[5]
```

```{r}
max_cost$solution[6]
```

```{r}
max_cost$solution[7]
```

```{r}
max_cost$solution[8]
```

```{r}
max_cost$solution[9]
```

